Automatically Splitting a Two-Stage Lambda Calculus

### 2015-10-14 paper/relatedwork.tex
small clarity fix re bifurcation

Researchers have explored other staging transformations that, 
like splitting, partition an input program into static and dynamic components.  
In particular, \emph{binding time separation}\,\cite{Mogensen89a} 
(also called \emph{program bifurcation}\,\cite{DeNiel91})
has been used as a preprocessor step in partial evaluators,
allowing more efficient specialization of programs with 
mixed-stage data structures without changes to the specializer itself.
Notably, the grammar-based binding-time specifications used in binding 
time separation were capable of describing
data structures with purely-static, purely-dynamic, and mixed stage
content, much like the type system of \lang\
(though this correspondence is less clear without our addition of 
\bbonep\ and $\curr$).

That said, unlike splitting, where the goal is to emit code where first stage results
are computed once and then reused in multiple invocations of second
stage execution, the second (dynamic) function produced by binding time separation
does not use the results of the first; instead,
%only serves as a preprocessing step for the subsequent
%specialization phase of partial evaluation.
it has access to the first stage inputs and recomputes all required
first stage computations. As noted by Knoblock and
Ruf\,\cite{knoblock96}, it may be possible to modify the program
bifurcation algorithm to cache and reuse the intermediate results, but
this was never attempted.

>>>>

Researchers have explored other staging transformations that, 
like splitting, partition an input two-stage program into two components,
on corresponding to each stage.  
In particular, \emph{binding time separation}\,\cite{Mogensen89a} 
(also called \emph{program bifurcation}\,\cite{DeNiel91})
has been used as a preprocessor step in partial evaluators,
allowing efficient specialization of programs with 
mixed-stage data structures without changes to the specializer itself.
Notably, the grammar-based binding-time specifications used in binding 
time separation were capable of describing
data structures with purely-static, purely-dynamic, and mixed stage
content, much like the type system of \lang\
(though this correspondence is less clear without our addition of 
\bbonep\ and $\curr$).

However unlike splitting, where the goal is to emit code where first stage results
are computed once and then reused in multiple invocations of second
stage execution, the second (dynamic) function produced by binding time separation
does not use the results of the first; instead,
%only serves as a preprocessing step for the subsequent
%specialization phase of partial evaluation.
it has access to the first stage inputs and recomputes all required
first stage computations. As noted by Knoblock and
Ruf\,\cite{knoblock96}, it may be possible to modify the program
bifurcation algorithm to cache and reuse the intermediate results, but
this was never attempted.
